---
title: "PVLDB"
author: "Donatus Herre (SLUB Dresden)"
subtitle: "Bibliometric Analysis"
pagetitle: "PVLDB :: Bibliometric Analysis"
author-meta: "SLUB Dresden"
date: "2025-07-25"
lang: "en-US"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: false
      smooth_scroll: false
    mathjax: null
    includes:
      after_body: assets/html/target.html
    keep_md: true
---

```{r setup, include=F}
knitr::opts_chunk$set(echo = FALSE, error = FALSE, message = FALSE, warning = FALSE)
knitr::opts_knit$set(root.dir = "..")
```

```{r functions}
mbsize <- function(path) format(round(file.info(path)$size/1000000, 2), nsmall=2)
kbsize <- function(path) format(round(file.info(path)$size/1000, 2), nsmall=2)
bsize <- function(path) file.info(path)$size
```

Branches: [main](https://github.com/slub/pvldb/tree/main) / [gh-pages](https://github.com/slub/pvldb/tree/gh-pages)

# Count Data

```{r crossref-raw-data}
cr_journal <- jsonlite::read_json("data/crossref_journals_2150-8097.json")
```

```{r openalex-raw-data}
oa_venue <- jsonlite::read_json("data/openalex_journals_V4210226185.json")
```

## Works

```{r crossref-works-count-data}
cr_works_count_by_year <- do.call("rbind", lapply(cr_journal$breakdowns$`dois-by-issued-year`, function(x) data.frame(year=x[[1]], count=as.integer(x[[2]]))))
```

```{r crossref-works-count-plot}
ggplot2::ggplot(cr_works_count_by_year, ggplot2::aes(year, count)) + ggplot2::geom_col() + ggplot2::scale_x_continuous(breaks=cr_works_count_by_year$year) + ggplot2::ggtitle("PVLDB Works Count (Crossref)") + ggplot2::xlab("") + ggplot2::ylab("")
```

```{r openalex-works-count-data}
oa_works_count_by_year <- do.call("rbind", lapply(oa_venue$counts_by_year, function(x) data.frame(year=x$year, count=as.integer(x$works_count))))
oa_works_count_by_year <- oa_works_count_by_year[oa_works_count_by_year$count > 0, ]
```

```{r openalex-works-count-plot}
ggplot2::ggplot(oa_works_count_by_year, ggplot2::aes(year, count)) + ggplot2::geom_col() + ggplot2::scale_x_continuous(breaks=oa_works_count_by_year$year) + ggplot2::ggtitle("PVLDB Works Count (OpenAlex)") + ggplot2::xlab("") + ggplot2::ylab("")
```

## Citations

```{r openalex-citations-count-data}
oa_citation_count_by_year <- do.call("rbind", lapply(oa_venue$counts_by_year, function(x) data.frame(year=x$year, count=as.integer(x$cited_by_count))))
```

```{r openalex-citations-count-plot}
ggplot2::ggplot(oa_citation_count_by_year, ggplot2::aes(year, count)) + ggplot2::geom_col() + ggplot2::scale_x_continuous(breaks=oa_citation_count_by_year$year) + ggplot2::ggtitle("PVLDB Citations Count (OpenAlex)") + ggplot2::xlab("") + ggplot2::ylab("")
```

```{r jcr-citations-count-data}
jcr_citation_count_by_year <- data.frame(year=c(2019, 2020, 2021, 2022, 2023, 2024), count=c(7166, 7198, 10242, 9139, 9665, 11647))
```

```{r jcr-citations-count-plot}
ggplot2::ggplot(jcr_citation_count_by_year, ggplot2::aes(year, count)) + ggplot2::geom_col() + ggplot2::scale_x_continuous(breaks=jcr_citation_count_by_year$year) + ggplot2::ggtitle("PVLDB Citations Count (2024 Journal Citation Reports © Clarivate, 2025)") + ggplot2::xlab("") + ggplot2::ylab("")
```

# Raw Data

- Crossref
  - [prefixes](./data/crossref_prefixes_10-14778.json) (`10.14778`) [JSON, `r bsize("public/data/crossref_prefixes_10-14778.json")` B]
  - [members](./data/crossref_members_5777.json) (`5777`) [JSON, `r kbsize("public/data/crossref_members_5777.json")` KB] + [members](./data/crossref_members_320.json) (`320`) [JSON, `r kbsize("public/data/crossref_members_320.json")` KB]
  - [journals](./data/crossref_journals_2150-8097.json) (`2150-8097`) [JSON, `r kbsize("public/data/crossref_journals_2150-8097.json")` KB]
  - [works](./data/crossref_works_filter-issn-2150-8097_works.json) (`filter=issn:2150-8097`) [JSON, `r mbsize("public/data/crossref_works_filter-issn-2150-8097_works.json")` MB]
    - [prefixes](./data/crossref_works_filter-issn-2150-8097_prefixes.json) [JSON, `r bsize("public/data/crossref_works_filter-issn-2150-8097_prefixes.json")` B]
    - [members](./data/crossref_works_filter-issn-2150-8097_members.json) [JSON, `r bsize("public/data/crossref_works_filter-issn-2150-8097_members.json")` B]
    - [dois](./data/crossref_works_filter-issn-2150-8097_dois.json) [JSON, `r kbsize("public/data/crossref_works_filter-issn-2150-8097_dois.json")` KB]
    - [dois-issue](./data/crossref_works_filter-issn-2150-8097_dois-issue.json) [JSON, `r kbsize("public/data/crossref_works_filter-issn-2150-8097_dois-issue.json")` KB]
    - [dois-article](./data/crossref_works_filter-issn-2150-8097_dois-article.json) [JSON, `r kbsize("public/data/crossref_works_filter-issn-2150-8097_dois-article.json")` KB]
    - [citation](./data/crossref_works_filter-issn-2150-8097_citation.json) [JSON, `r mbsize("public/data/crossref_works_filter-issn-2150-8097_citation.json")` MB] (via OpenCitations)
      - [dois](./data/crossref_works_filter-issn-2150-8097_dois-citation.json) [JSON, `r mbsize("public/data/crossref_works_filter-issn-2150-8097_dois-citation.json")` MB]
      - [issns](./data/crossref_works_filter-issn-2150-8097_issns-citation.json) [JSON, `r kbsize("public/data/crossref_works_filter-issn-2150-8097_issns-citation.json")` KB]
      - [count-issns](./data/crossref_works_filter-issn-2150-8097_count-issns-citation.json) [JSON, `r kbsize("public/data/crossref_works_filter-issn-2150-8097_count-issns-citation.json")` KB]
      - [count-issns](./data/crossref_works_filter-issn-2150-8097_count-issns-citation.csv) [CSV, `r kbsize("public/data/crossref_works_filter-issn-2150-8097_count-issns-citation.csv")` KB] (enriched via OpenAlex)
      - [year-types](./data/crossref_works_filter-issn-2150-8097_year-types-citation.json) [JSON, `r mbsize("public/data/crossref_works_filter-issn-2150-8097_year-types-citation.json")` MB]
    - [count-citation](./data/crossref_works_filter-issn-2150-8097_count-citation.json) [JSON, `r kbsize("public/data/crossref_works_filter-issn-2150-8097_count-citation.json")` KB] (via OpenCitations)
    - [reference](./data/crossref_works_filter-issn-2150-8097_reference.json) [JSON, `r mbsize("public/data/crossref_works_filter-issn-2150-8097_reference.json")` MB]
      - [dois](./data/crossref_works_filter-issn-2150-8097_dois-reference.json) [JSON, `r mbsize("public/data/crossref_works_filter-issn-2150-8097_dois-reference.json")` MB]
      - [issns](./data/crossref_works_filter-issn-2150-8097_issns-reference.json) [JSON, `r kbsize("public/data/crossref_works_filter-issn-2150-8097_issns-reference.json")` KB]
      - [count-issns](./data/crossref_works_filter-issn-2150-8097_count-issns-reference.json) [JSON, `r kbsize("public/data/crossref_works_filter-issn-2150-8097_count-issns-reference.json")` KB]
      - [count-issns](./data/crossref_works_filter-issn-2150-8097_count-issns-reference.csv) [CSV, `r kbsize("public/data/crossref_works_filter-issn-2150-8097_count-issns-reference.csv")` KB] (enriched via OpenAlex)
      - [year-types](./data/crossref_works_filter-issn-2150-8097_year-types-reference.json) [JSON, `r mbsize("public/data/crossref_works_filter-issn-2150-8097_year-types-reference.json")` MB]
    - [count-reference](./data/crossref_works_filter-issn-2150-8097_count-reference.json) [JSON, `r kbsize("public/data/crossref_works_filter-issn-2150-8097_count-reference.json")` KB]
    - [year-types](./data/crossref_works_filter-issn-2150-8097_year-types.json) [JSON, `r kbsize("public/data/crossref_works_filter-issn-2150-8097_year-types.json")` KB]
- OpenAlex
  - [sources](./data/openalex_journals_V4210226185.json) (`S4210226185`) [JSON, `r kbsize("public/data/openalex_journals_V4210226185.json")` KB]

# Data Sources

- [Crossref API](https://api.crossref.org)
  - members
    - [320](https://api.crossref.org/members/320?mailto=bibliometrie@slub-dresden.de)
    - [5777](https://api.crossref.org/members/5777?mailto=bibliometrie@slub-dresden.de)
  - prefixes
    - [10.14778](https://api.crossref.org/prefixes/10.14778?mailto=bibliometrie@slub-dresden.de)
  - journals
    - [2150-8097](https://api.crossref.org/journals/2150-8097?mailto=bibliometrie@slub-dresden.de)
  - works
    - [filter=issn:2150-8097](https://api.crossref.org/works?filter=issn:2150-8097&mailto=bibliometrie@slub-dresden.de)
- [OpenCitations API](https://opencitations.net/index/coci/api/v1) (COCI)
  - citations
- [OpenAlex API](https://docs.openalex.org)
  - sources
    - [S4210226185](https://api.openalex.org/sources/S4210226185?mailto=bibliometrie@slub-dresden.de)
  - works
    - [filter=primary_location.source.id:S4210226185](https://api.openalex.org/works?filter=primary_location.source.id:S4210226185&mailto=bibliometrie@slub-dresden.de)

# Content Access

- VLDB Endowment
  - [PVLDB (Proceedings of the VLDB Endowment)](https://vldb.org/pvldb/)
- ACM DL > Collections > Hosted Content
    - [Proceedings of the VLDB Endowment](https://dl.acm.org/journal/pvldb)
- DBLP > Journals
    - [Proceedings of the VLDB Endowment](https://dblp.org/db/journals/pvldb/)

# Usage Terms

[![Creative Commons License](https://mirrors.creativecommons.org/presskit/buttons/80x15/svg/by.svg)](http://creativecommons.org/licenses/by/4.0/) This [document](#) is licensed under a [Creative Commons Attribution 4.0 International License](./LICENSE.txt).  
[![Public Domain Dedication](https://mirrors.creativecommons.org/presskit/buttons/80x15/svg/cc-zero.svg)](https://creativecommons.org/publicdomain/zero/1.0/) The [raw data](#raw-data) is made available under the [CC0 1.0 Universal Public Domain Dedication](./data/LICENSE.txt).
