---
title: "PVLDB"
subtitle: "Bibliometric Analysis"
pagetitle: "PVLDB :: Bibliometric Analysis"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
lang: "en-US"
output:
  html_document:
    mathjax: null
    includes:
      after_body: assets/html/target.html
    keep_md: true
---

```{r setup, include=F}
knitr::opts_chunk$set(echo = FALSE, error = FALSE, message = FALSE, warning = FALSE)
knitr::opts_knit$set(root.dir = "..")
```

```{r functions}
mbsize <- function(path) format(round(file.info(path)$size/1000000, 2), nsmall=2)
kbsize <- function(path) format(round(file.info(path)$size/1000, 2), nsmall=2)
```

# Count Data

```{r openalex-raw-data}
oa_venue <- jsonlite::read_json("https://api.openalex.org/journals/V4210226185?mailto=bibliometrie@slub-dresden.de")
```

```{r crossref-raw-data}
cr_journal <- jsonlite::read_json("https://api.crossref.org/journals/2150-8097?mailto=bibliometrie@slub-dresden.de")
```

## Works

```{r crossref-works-count-data}
cr_works_count_by_year <- do.call("rbind", lapply(cr_journal$message$breakdowns$`dois-by-issued-year`, function(x) data.frame(year=x[[1]], count=as.integer(x[[2]]))))
```

```{r crossref-works-count-plot}
ggplot2::ggplot(cr_works_count_by_year, ggplot2::aes(year, count)) + ggplot2::geom_col() + ggplot2::scale_x_continuous(breaks=rev(cr_works_count_by_year$year)) + ggplot2::ggtitle("PVLDB Works Count (Crossref)") + ggplot2::xlab("") + ggplot2::ylab("")
```

```{r openalex-works-count-data}
oa_works_count_by_year <- do.call("rbind", lapply(oa_venue$counts_by_year, function(x) data.frame(year=x$year, count=as.integer(x$works_count))))
```

```{r openalex-works-count-plot}
ggplot2::ggplot(oa_works_count_by_year, ggplot2::aes(year, count)) + ggplot2::geom_col() + ggplot2::scale_x_continuous(breaks=rev(oa_works_count_by_year$year)) + ggplot2::ggtitle("PVLDB Works Count (OpenAlex)") + ggplot2::xlab("") + ggplot2::ylab("")
```

## Citations

```{r openalex-citations-count-data}
oa_citation_count_by_year <- do.call("rbind", lapply(oa_venue$counts_by_year, function(x) data.frame(year=x$year, count=as.integer(x$cited_by_count))))
```

```{r openalex-citations-count-plot}
ggplot2::ggplot(oa_citation_count_by_year, ggplot2::aes(year, count)) + ggplot2::geom_col() + ggplot2::scale_x_continuous(breaks=rev(oa_citation_count_by_year$year)) + ggplot2::ggtitle("PVLDB Citations Count (OpenAlex)") + ggplot2::xlab("") + ggplot2::ylab("")
```

```{r jcr-citations-count-data}
jcr_citation_count_by_year <- data.frame(year=c(2019, 2020, 2021), count=c(7166, 7198, 10242))
```

```{r jcr-citations-count-plot}
ggplot2::ggplot(jcr_citation_count_by_year, ggplot2::aes(year, count)) + ggplot2::geom_col() + ggplot2::scale_x_continuous(breaks=rev(jcr_citation_count_by_year$year)) + ggplot2::ggtitle("PVLDB Citations Count (2021 Journal Citation Reports © Clarivate, 2022)") + ggplot2::xlab("") + ggplot2::ylab("")
```

# Raw Data

- Crossref
  - [works](./data/crossref_works_filter-issn-2150-8097.json) (`filter=issn:2150-8097`) [JSON, `r mbsize("public/data/crossref_works_filter-issn-2150-8097.json")` MB]
    - [dois](./data/crossref_works_filter-issn-2150-8097_dois.json) [JSON, `r kbsize("public/data/crossref_works_filter-issn-2150-8097_dois.json")` KB]
    - [reference-dois](./data/crossref_works_filter-issn-2150-8097_reference-dois.json) [JSON, `r mbsize("public/data/crossref_works_filter-issn-2150-8097_reference-dois.json")` MB]
    - [year-types](./data/crossref_works_filter-issn-2150-8097_year-types.json) [JSON, `r kbsize("public/data/crossref_works_filter-issn-2150-8097_year-types.json")` KB]

# Data Sources

- [Crossref API](https://api.crossref.org)
  - members
    - [320](https://api.crossref.org/members/320?mailto=bibliometrie@slub-dresden.de)
    - [5777](https://api.crossref.org/members/5777?mailto=bibliometrie@slub-dresden.de)
  - prefixes
    - [10.1145](https://api.crossref.org/prefixes/10.1145?mailto=bibliometrie@slub-dresden.de)
    - [10.14778](https://api.crossref.org/prefixes/10.14778?mailto=bibliometrie@slub-dresden.de)
  - journals
    - [2150-8097](https://api.crossref.org/journals/2150-8097?mailto=bibliometrie@slub-dresden.de)
  - works
    - [filter=issn:2150-8097](https://api.crossref.org/works?filter=issn:2150-8097&mailto=bibliometrie@slub-dresden.de)
    - [filter=issn:2150-8097,has-abstract:true](https://api.crossref.org/works?filter=issn:2150-8097,has-abstract:true&mailto=bibliometrie@slub-dresden.de)
    - [filter=issn:2150-8097,has-references:true](https://api.crossref.org/works?filter=issn:2150-8097,has-references:true&mailto=bibliometrie@slub-dresden.de)
    - [filter=issn:2150-8097&facet=type-name:*](https://api.crossref.org/works?filter=issn:2150-8097&facet=type-name:*&rows=0&mailto=bibliometrie@slub-dresden.de)
    - [filter=issn:2150-8097,type:journal-article](https://api.crossref.org/works?filter=issn:2150-8097,type:journal-article&mailto=bibliometrie@slub-dresden.de)
    - [filter=issn:2150-8097,type:journal-article,has-references:true](https://api.crossref.org/works?filter=issn:2150-8097,type:journal-article,has-references:true&mailto=bibliometrie@slub-dresden.de)
- [OpenAlex API](https://docs.openalex.org/api)
  - venues
    - [V4210226185](https://api.openalex.org/journals/V4210226185?mailto=bibliometrie@slub-dresden.de) / [issn:2150-8097](https://api.openalex.org/journals/issn:2150-8097?mailto=bibliometrie@slub-dresden.de)
  - works
    - [filter=host_venue.id:V4210226185](https://api.openalex.org/works?filter=host_venue.id:V4210226185&mailto=bibliometrie@slub-dresden.de)
    - [filter=host_venue.id:V4210226185&group_by=type](https://api.openalex.org/works?filter=host_venue.id:V4210226185&group_by=type&mailto=bibliometrie@slub-dresden.de)
    - [filter=host_venue.id:V4210226185&group_by=publication_year](https://api.openalex.org/works?filter=host_venue.id:V4210226185&group_by=publication_year&mailto=bibliometrie@slub-dresden.de)
- [OpenCitations API](https://opencitations.net/index/coci/api/v1) (COCI)
  - citations

# Content Access

- ACM DL
  - Journals
    - [Proceedings of the VLDB Endowment](https://dl.acm.org/journal/pvldb)
- DBLP
  - Journals
    - [Proceedings of the VLDB Endowment](https://dblp.org/db/journals/pvldb/)
- VLDB Endowment
  - [PVLDB (Proceedings of the VLDB Endowment)](https://vldb.org/pvldb/)
