---
title: "PVLDB"
author: "Donatus Herre (SLUB Dresden)"
subtitle: "Bibliometric Analysis"
pagetitle: "PVLDB :: Bibliometric Analysis :: Outtakes"
author-meta: "SLUB Dresden"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
lang: "en-US"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: false
      smooth_scroll: false
    mathjax: null
    includes:
      after_body: assets/html/target.html
    keep_md: true
---

```{r setup, include=F}
knitr::opts_chunk$set(echo = FALSE, error = FALSE, message = FALSE, warning = FALSE)
knitr::opts_knit$set(root.dir = "..")
```

```{r functions}
mbsize <- function(path) format(round(file.info(path)$size/1000000, 2), nsmall=2)
kbsize <- function(path) format(round(file.info(path)$size/1000, 2), nsmall=2)
bsize <- function(path) file.info(path)$size
```

Branches: [main](https://github.com/slub/pvldb/tree/main) / [gh-pages](https://github.com/slub/pvldb/tree/gh-pages)

# Count Data

```{r journalsdb-raw-data}
jdb_journal <- jsonlite::read_json("data/journalsdb_journals_2150-8097.json")
```

## Works

```{r journalsdb-works-count-data}
jdb_works_count_by_year <- do.call("rbind", lapply(jdb_journal$dois_by_issued_year, function(x) data.frame(year=x[[1]], count=as.integer(x[[2]]))))
```

```{r journalsdb-works-count-plot}
ggplot2::ggplot(jdb_works_count_by_year, ggplot2::aes(year, count)) + ggplot2::geom_col() + ggplot2::scale_x_continuous(breaks=jdb_works_count_by_year$year) + ggplot2::ggtitle("PVLDB Works Count (JournalsDB)") + ggplot2::xlab("") + ggplot2::ylab("")
```

```{r wos-works-count-data}
wos_works_count_by_year <- data.frame(
  year=c(2008, 2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019, 2020, 2021, 2022, 2023, 2024),
  count=c(168, 167, 198, 188, 194, 251, 243, 229, 183, 207, 207, 234, 297, 356, 368, 382, 401)
) # date updated: 2025-07-22
```

```{r wos-works-count-plot}
ggplot2::ggplot(wos_works_count_by_year, ggplot2::aes(year, count)) + ggplot2::geom_col() + ggplot2::scale_x_continuous(breaks=wos_works_count_by_year$year) + ggplot2::ggtitle("PVLDB Works Count (2025-07-22 Web of Science © Clarivate, 2025)") + ggplot2::xlab("") + ggplot2::ylab("")
```

```{r citescore-works-count-data}
citescore_works_count <- data.frame(
  year=c(2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019, 2020, 2021, 2022, 2023, 2024),
  count=c(456, 705, 784, 767, 807, 750, 782, 756, 727, 800, 960, 1031, 1376, 1405)
) # date-updated: 2025-07-22 (2024-2022) 2022-05-30 (2021) 2021-11-09 (2011-2020)
```

```{r citescore-works-count-plot, eval=F}
ggplot2::ggplot(citescore_works_count, ggplot2::aes(year, count)) + ggplot2::geom_col() + ggplot2::scale_x_continuous(breaks=citescore_works_count$year) + ggplot2::ggtitle("PVLDB Works Count (2024 CiteScore © Elsevier, 2025)") + ggplot2::xlab("") + ggplot2::ylab("")
```

```{r scival-works-count-data}
scival_works_count <- data.frame(
  year=c(2008, 2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019, 2020, 2021, 2022, 2023, 2024),
  count=c(166, 167, 194, 188, 196, 261, 252, 258, 183, 184, 404, 29, 343, 363, 349, 388, 368)
) # date-updated: 2025-07-22 (2019-2024) 2022-10-23 (2012-2021)
```

```{r scival-works-count-plot}
ggplot2::ggplot(scival_works_count, ggplot2::aes(year, count)) + ggplot2::geom_col() + ggplot2::scale_x_continuous(breaks=scival_works_count$year) + ggplot2::ggtitle("PVLDB Works Count (2025-07-22 SciVal © Elsevier, 2025)") + ggplot2::xlab("") + ggplot2::ylab("")
```

## Citations

```{r wos-citations-count-data}
wos_citation_count_by_year <- data.frame(
  year=c(2008, 2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019, 2020, 2021, 2022, 2023, 2024),
  count=c(7415, 4544, 8334, 7979, 10532, 8571, 8967, 9078, 5413, 8072, 5494, 5351, 6421, 3957, 3161, 1515, 321)
) # date updated: 2025-07-22
```

```{r wos-citations-count-plot}
ggplot2::ggplot(wos_citation_count_by_year, ggplot2::aes(year, count)) + ggplot2::geom_col() + ggplot2::scale_x_continuous(breaks=wos_citation_count_by_year$year) + ggplot2::ggtitle("PVLDB Citations Count (2025-07-22 Web of Science © Clarivate, 2025)") + ggplot2::xlab("Publication Year of Cited Work") + ggplot2::ylab("")
```

```{r citescore-citations-count-data}
citescore_citation_count <- data.frame(
  year=c(2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019, 2020, 2021, 2022, 2023, 2024),
  count=c(3608, 4700, 5417, 5122, 6067, 6033, 6040, 5665, 5802, 5937, 6726, 5521, 10552, 9860)
) # date-updated: 2025-07-22 (2024-2022) 2022-05-30 (2021) 2021-11-09 (2011-2020)
```

```{r citescore-citations-count-plot, eval=F}
ggplot2::ggplot(citescore_citation_count, ggplot2::aes(year, count)) + ggplot2::geom_col() + ggplot2::scale_x_continuous(breaks=citescore_citation_count$year) + ggplot2::ggtitle("PVLDB Citations Count (2024 CiteScore © Elsevier, 2025)") + ggplot2::xlab("") + ggplot2::ylab("")
```

```{r scival-citations-count-data}
scival_citation_count <- data.frame(
  year=c(2008, 2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019, 2020, 2021, 2022, 2023, 2024, 2025),
  count=c(13195, 14110, 13710, 12459, 15211, 12349, 12665, 10884, 9883, 8296, 12679, 997, 10287, 5866, 4282, 2495, 659, 23)
) # date-updated: 2025-07-22
```

```{r scival-citations-count-plot}
ggplot2::ggplot(scival_citation_count, ggplot2::aes(year, count)) + ggplot2::geom_col() + ggplot2::scale_x_continuous(breaks=scival_citation_count$year) + ggplot2::ggtitle("PVLDB Citations Count (2025-07-22 SciVal © Elsevier, 2025)") + ggplot2::xlab("Publication Year of Cited Work") + ggplot2::ylab("")
```

# Raw Data

- JournalsDB (last update: 2025-07-22)
  - [journals](./data/journalsdb_journals_2150-8097.json) (`2150-8097`) [JSON, `r kbsize("public/data/journalsdb_journals_2150-8097.json")` KB]

# Data Sources

- [Crossref API](https://api.crossref.org)
  - prefixes
    - [10.1145](https://api.crossref.org/prefixes/10.1145?mailto=bibliometrie@slub-dresden.de)
  - works
    - [filter=issn:2150-8097,has-abstract:true](https://api.crossref.org/works?filter=issn:2150-8097,has-abstract:true&mailto=bibliometrie@slub-dresden.de)
    - [filter=issn:2150-8097,has-references:true](https://api.crossref.org/works?filter=issn:2150-8097,has-references:true&mailto=bibliometrie@slub-dresden.de)
    - [filter=issn:2150-8097&facet=type-name:*](https://api.crossref.org/works?filter=issn:2150-8097&facet=type-name:*&rows=0&mailto=bibliometrie@slub-dresden.de)
    - [filter=issn:2150-8097,type:journal-article](https://api.crossref.org/works?filter=issn:2150-8097,type:journal-article&mailto=bibliometrie@slub-dresden.de)
    - [filter=issn:2150-8097,type:journal-article,has-references:true](https://api.crossref.org/works?filter=issn:2150-8097,type:journal-article,has-references:true&mailto=bibliometrie@slub-dresden.de)
    - [filter=issn:2150-8097&select=DOI,is-referenced-by-count](https://api.crossref.org/works?filter=issn:2150-8097&select=DOI,is-referenced-by-count&mailto=bibliometrie@slub-dresden.de)
- [Crossref OAI](https://oai.crossref.org/oai?verb=Identify)
  - ListSets
    - [set=J:10.14778](https://oai.crossref.org/oai?verb=ListSets&set=J:10.14778)
- [Crossref Depositor Report](https://www.crossref.org/documentation/reports/depositor-report/)
  - journals
    - [pubid=J249417](https://data.crossref.org/depositorreport?pubid=J249417)
- [Crossref Event Data API](https://www.eventdata.crossref.org/)
  - events
    - [obj-id.prefix=10.14778](https://api.eventdata.crossref.org/v1/events?obj-id.prefix=10.14778&mailto=bibliometrie@slub-dresden.de)
    - [subj-id.prefix=10.14778](https://api.eventdata.crossref.org/v1/events?subj-id.prefix=10.14778&mailto=bibliometrie@slub-dresden.de)
- [DataCite API](https://support.datacite.org/docs/api)
  - dois
    - [query=relatedIdentifiers.relatedIdentifier:10.14778*](https://api.datacite.org/dois?query=relatedIdentifiers.relatedIdentifier:10.14778*)
    - [query=relatedIdentifiers.relatedIdentifier:10.14778*&affiliation=true](https://api.datacite.org/dois?query=relatedIdentifiers.relatedIdentifier:10.14778*&affiliation=true)
    - [query=relatedIdentifiers.relatedIdentifier:10.14778*&affiliation=true&resource-type-id=dataset](https://api.datacite.org/dois?query=relatedIdentifiers.relatedIdentifier:10.14778*&affiliation=true&resource-type-id=dataset)
- [DBLP API](https://dblp.org/faq/13501473.html)
  - search/publ/api
    - [streams/journals/pvldb](https://dblp.org/search/publ/api?q=stream%3Astreams%2Fjournals%2Fpvldb%3A&h=1000&format=json)
  - search/venue/api
    - [q=Proceedings of the VLDB Endowment](https://dblp.org/search/venue/api?q=Proceedings%20of%20the%20VLDB%20Endowment&format=json)
- [ISSN Portal LD Service](https://www.issn.org/understanding-the-issn/assignment-rules/issn-linked-data-application-profile/)
  - resource/ISSN
    - [2150-8097](https://portal.issn.org/resource/ISSN/2150-8097?format=json)
  - resource/ISSN-L
    - [2150-8097](https://portal.issn.org/resource/ISSN-L/2150-8097?format=json)
- [JournalsDB API](https://api.journalsdb.org/apidocs/)
  - journals
    - [2150-8097](https://api.journalsdb.org/journals/2150-8097)
- [Wikidata](https://www.wikidata.org/wiki/Wikidata:Data_access)
  - Linked Data Interface
    - [Q27722874](https://www.wikidata.org/wiki/Special:EntityData/Q27722874.json)
- [SLUB LOD API](https://data.slub-dresden.de/)
  - resource
    - [591517426](https://data.slub-dresden.de/resources/591517426)
  - source/kxp-de14
    - [591517426](https://data.slub-dresden.de/source/kxp-de14/591517426)

# Usage Terms

[![Creative Commons License](https://mirrors.creativecommons.org/presskit/buttons/80x15/svg/by.svg)](http://creativecommons.org/licenses/by/4.0/) This [document](#) is licensed under a [Creative Commons Attribution 4.0 International License](./LICENSE.txt).  
[![Public Domain Dedication](https://mirrors.creativecommons.org/presskit/buttons/80x15/svg/cc-zero.svg)](https://creativecommons.org/publicdomain/zero/1.0/) The [raw data](#raw-data) is made available under the [CC0 1.0 Universal Public Domain Dedication](./data/LICENSE.txt).
