---
title: "PVLDB"
author: "Donatus Herre (SLUB Dresden)"
subtitle: "Bibliometric Analysis"
pagetitle: "PVLDB :: Bibliometric Analysis"
author-meta: "SLUB Dresden"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
lang: "en-US"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float:
      collapsed: false
      smooth_scroll: false
    mathjax: null
    includes:
      after_body: assets/html/target.html
    keep_md: true
---

```{r setup, include=F}
knitr::opts_chunk$set(echo = FALSE, error = FALSE, message = FALSE, warning = FALSE)
knitr::opts_knit$set(root.dir = "..")
```

```{r functions}
mbsize <- function(path) format(round(file.info(path)$size/1000000, 2), nsmall=2)
kbsize <- function(path) format(round(file.info(path)$size/1000, 2), nsmall=2)
bsize <- function(path) file.info(path)$size
```

Branches: [main](https://github.com/slub/pvldb/tree/main) / [gh-pages](https://github.com/slub/pvldb/tree/gh-pages)

# Count Data

```{r journalsdb-raw-data}
jdb_journal <- jsonlite::read_json("data/journalsdb_journals_2150-8097.json")
```

## Works

```{r journalsdb-works-count-data}
jdb_works_count_by_year <- do.call("rbind", lapply(jdb_journal$dois_by_issued_year, function(x) data.frame(year=x[[1]], count=as.integer(x[[2]]))))
```

```{r journalsdb-works-count-plot}
ggplot2::ggplot(jdb_works_count_by_year, ggplot2::aes(year, count)) + ggplot2::geom_col() + ggplot2::scale_x_continuous(breaks=jdb_works_count_by_year$year) + ggplot2::ggtitle("PVLDB Works Count (JournalsDB)") + ggplot2::xlab("") + ggplot2::ylab("")
```

## Citations

...

# Raw Data

- JournalsDB (last update: 2022-10-17)
  - [journals](./data/journalsdb_journals_2150-8097.json) (`2150-8097`) [JSON, `r kbsize("public/data/journalsdb_journals_2150-8097.json")` KB]

# Data Sources

- [JournalsDB API](https://api.journalsdb.org/apidocs/)
  - journals
    - [2150-8097](https://api.journalsdb.org/journals/2150-8097)

# Usage Terms

[![Creative Commons License](https://mirrors.creativecommons.org/presskit/buttons/80x15/svg/by.svg)](http://creativecommons.org/licenses/by/4.0/) This [report](#) is licensed under a [Creative Commons Attribution 4.0 International License](./LICENSE.txt).  
[![Public Domain Dedication](https://mirrors.creativecommons.org/presskit/buttons/80x15/svg/cc-zero.svg)](https://creativecommons.org/publicdomain/zero/1.0/) The [raw data](#raw-data) is made available under the [CC0 1.0 Universal Public Domain Dedication](./data/LICENSE.txt).
